---
title: "p8105_hw1_zc2443"
author: "Ziyang Chen zc2443"
date: 2019-09-14
output: github_document
---

```{r Prblem1, message=FALSE}
library(tidyverse)

set.seed(1)
df = tibble(
  ran_samp = rnorm(8), #create random sample of size 8 from a standard Normal distribution
  ran_samp_pos = ran_samp > 0, #a logical vector indicating whether elements of the sample are greater than 0
  char_vec = c("p8105","is","so","funny","ziyang","chen","the","brilliant"), #create a character vector of length 8
  some_vec = c("low","medium","high","low","medium","high","low","high"), #create vector of length 8, with 3 different factor “levels”
  fac_vec = factor(some_vec) #make the above vector to be a factor vector
)

mean(df$ran_samp)
mean(df$ran_samp_pos)
mean(df$char_vec)
mean(df$fac_vec)
```

When I took the mean values of each variable, the numeric and the logical variables worked while the character and the factor variables didn't work.

```{r Problem1,eval=FALSE}
as.numeric(df$ran_samp_pos) #convert the logical vector to a numeric vector
as.numeric(df$char_vec) #convert the character vector to a numeric vector
as.numeric(df$fac_vec) #convert the factor vector to a numeric vector
```

For the logical vector, it was successfully converted to a numeric vector since the origin values of this vector consists of 0 and 1 which are already numeric values. For the character and the factor vectors, they failed to be converted to numeric vectors since they are not consist of numeric values. Hence, we can take the mean value of a numeric value based vector but we cannot take the mean value of a character vector or a factor vector.

```{r}
as.numeric(df$ran_samp_pos)*df$ran_samp
factor(df$ran_samp_pos)*df$ran_samp
as.numeric(factor(df$ran_samp_pos))*df$ran_samp
```

